Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-06-16 write-up/covid-writeup.tex
Update covid-writeup.tex

Many states also provide aggregate demographic information on those who requested a test as well as those who tested positive for SARS-CoV-2. Indiana's \href{https://www.coronavirus.in.gov/2393.htm}{COVID-19 dashboard}, for instance, provides statewide demographics for age, gender, ethnicity, and race.  The demographic information is based on cumulative testing.  In addition, the Regenstrief Institute provides additional comorbidity information among those who tested positive for COVID-19 in the state of Indiana, including hypertension, diabetes, and chronic obstructive pulmonary disease (COPD) summary statistics. These comprise the main set of covariate information available from public sources for Indiana. Similar demographic information is likely available for other states.
% https://www.regenstrief.org/covid-dashboard/
%

>>>>

Many states do not provide any demographic information on who requested a test nor on who tested positive for SARS-CoV-2. Working closely with the State of Indiana, the author's were able to request public availability of COVID-19 total tests, positive tests, and related deaths per day broken out marginally by age, gender, ethnicity, and race.  Similar demographic breakdowns may be available for other states, but to date the data has not been made publicly available at the daily level.
% https://www.regenstrief.org/covid-dashboard/
%
